% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
% Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This cover letter is for the position
% http://hire.jobvite.com/CompanyJobs/Careers.aspx?c=qb19Vfw0&j=oVRi2fwQ&nl=1&page=Job%20Description&s=LINKEDIN
% Intern - Modeling and Data Science
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Input header file 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../../CV_Resume/HeaderfileTexLetter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8.5in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Subhrangshu Nandi}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}
{Hiring Manager \\
Engineering, \\
Quantcast, \\
San Francisco, CA
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Description
%% 10-12 week summer internship program (~June – August 2016)
%% Opportunity to receive offer for full-time employment following internship
%% Fast-paced environment with friendly, hard working colleagues
%% Competitive pay with housing and travel assistance
%% Solve real problems, build products and leave an impact on the company
%% Gain industry experience in machine learning, statistics and software engineering
%% Modeling study groups and technical roundtables
%% Perks include free lunch and dinner, Friday company happy hour, intern social events and executive leadership team speaker series
%% Requirements

%% Currently pursuing Master’s or PhD degree in computer science, software engineering, electrical engineering, machine learning, mathematics, statistics, or related field
%% Graduation date between Dec 2016 and June 2018
%% Passion and curiosity for modeling and data science
%% Excellent command of one or more programming languages; preferably Java or Python
%% Excellent command of algorithms, statistics, machine learning and/or optimization
%% Exceptional communication skills (verbal, written and presentation)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{flushleft}
{\bf Subhrangshu Nandi}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill 1300 University Ave, Suite 1250D, Madison, WI 53706 \\
\hfill snandi@wisc.edu, nands31@gmail.com\\
\hfill (413) 530-1400 or (608) 284-8308
\end{flushright} 
\vfill % forces letterhead to top of page

\opening{Dear Hiring Manager:} 
 
\noindent %PARAGRAPH ONE: State reason for letter, name the position or type of work you are applying for and identify source from  which  you learned   of   the  opening.  (i.e.  Career  Development  Center, newspaper, employment service, personal contact). 
I am a statistics Ph.D. student looking for a summer internship opportunity, starting in June 2016. I would like to apply for ``Intern - Modeling and Data Science'' position at Quantcast. I came across the position on Linkedin.
 
\noindent %PARAGRAPH  TWO:  Indicate why you are interested in the position, the company, its products, services - above all, stress what  you can  do  for  the employer. If you are a recent graduate, explain how your academic background makes you a qualified candidate  for the  position.  If  you have practical work experience, point out specific achievements or unique qualifications. Try not to repeat the  same  information  the reader will find in the resume. Refer the reader to the enclosed resume or application which summarizes your  qualifications,  training,  and experiences. The purpose of this section is to strengthen your resume  by  providing  details which bring your experiences to life. 
I have a combined experience of seven years in the statistical consulting and quantitave trading industries, before coming back to graduate school. As a statistics Ph.D. student, I have trained in theoretical and computational aspects of statistics and machine learning. I would like to leverage my data science background to address real problems pertaining to improving daily lives. I believe a data scientist should be involved in all four stages of data analysis: (1) understanding of the data generation mechanism, along with the assumptions and limitations; (2) cleaning and pre-processing the data; (3) analyzing the data to answer the hypotheses; (4) visualize the results and different scenarios. I have academic and industry experience in all the above stages of data analysis. I have experience of handling large datasets (several GBs), including high-throughput and high-performance computing on the \href{http://www.opensciencegrid.org/}{open science grid}. I have experience in most distributions of unix, and often use classical unix programs such as sed, vi, bash, for efficient data mining. Data science is far beyond applying a few statistics and machine learning algorithms and my arsenal of skills is well rounded to be an efficient data scientist. 

In addition to my doctoral education in statistics, my experiences in consulting and quantitative trading provide me a competitive edge. I have experience working and leading teams of different sizes. I excel in projects with aggressive deadlines. I also enjoy exploratory research projects that intend to push the boundary of human knowledge outward, which is one of the reasons why I returned to graduate school. I am innovative, diligent, hard-working and persistent. 

\noindent %PARAGRAPH THREE: Request a personal interview and  indicate  your flexibility as to the time and place. Repeat your phone number in the letter and offer assistance to help in a speedy response. For example,  state that you will be in the city where the company is located on a certain date and would like to set up an  interview. Or,  state  that  you  will  call  on a certain date to set up an interview. End the letter by thanking  the  employer  for  taking time to consider your credentials. 
I enjoy working in an dynamic environment like that of Quantcast's, finding creative solutions to complex problems in efficient manner. I will be a great fit for the Modeling and Data Science Intern position at Quantcast. I am available for a phone interview on most weekdays. 

Thank you for your time and considering my candidacy. 
 
\closing{Sincerely yours,} 
 
 
%\encl{}  				% Enclosures

\end{letter}

\end{document}

